Fictitious Play in Network Aggregative Games

### 2021-04-29 Documents/FP in NAGs/FPNAG.tex
Included Expt

\theoremstyle{definition}
\newtheorem*{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{assumption}{Assumption}

@@

@@

	\begin{enumerate}
		\item Introduction: Explain the notion of a Network Aggregative Game, and Fictitious Play
		with literature on the state of the art. Assumptions made as well as summary of results
		\item Maybe? Relation with the model of Grammatico
		\item Preliminaries \begin{itemize}
			\item The Network Aggregative Game model
			\item Fictitious Play, as well as the CTFP property
		\end{itemize}
		\item Convergence of Fictitious Play \begin{itemize}
			\item Existence of the Nash Equilibrium
			\item Existence of a CTFP
			\item Convergence of CTFP to a fixed point
			\item Corrolary: when $w_{ii} = 0$ (i.e. the interaction graph is simple) CTFP converges
			to a NE
			\item Convergence of CTFP to the NA-CCE set
		\end{itemize}
		\item Numerical Experiments \begin{itemize}
			\item Non-convergent examples
			\item Fictitious Play with Noise
		\end{itemize}
		\item Discussion of Experiments
		\item Concluding Remarks
	\end{enumerate}

@@

	As a network game, each agent $\mu$ has an associated set of
        actions $\actionset{\mu}$ which has cardinality
        $|\actionset{\mu}| = n$. \fb{what is a strategy then? how can
          we define them if we didn't introduce actions?}

        We can construct the \fb{unit-simplex ?} on the action
        set as $\Delta_\mu := \{\xmu \in \mathbb{R}^n \, : \, \sum_i
        \xmuaction{i} = 1\}$ where $\xmuaction{i}$ is the probability
        with which agent $\mu$ plays the action $i$. As such we
        refer to $\xmu$ as the \emph{state} of agent $\mu$ (this is
        often referred to as $\mu$'s mixed strategy). Also associated
        with each agent is a utility function $u^\mu(\xmu, \xnotmu)$
        in which we use the standard notation $-\mu$ to refer to all
        agents other than $\mu$. Notice that this requires that each
        agent plays the same strategy against all of their neighbours.

	With all of the above definitions, we can formalise the
        network aggregative (NA) game:

	\begin{definition}[Network Aggregative Game]
		A Network Aggregative game is defined as the tuple $\Gamma =
        (I, (\actionset{\mu},
        \utility{\mu})_{\mu \in \mathcal{N}})$, where $I$ is the interaction graph, $\actionset{\mu}$ and $\utility{\mu}$ refer to the set of
        actions and the utility function of agent $\mu$ respectively.
	\end{definition}

	What is unique about the NA game is the structure of the
        payoffs themselves. In this format, each agent is receives a
        reference $\sigma$ which is a weighted sum of each of their
        neighbours state. Formally
%
	\begin{equation}
		\sigma^\mu = \sum_{\nu \in N^\mu} \wmunu \xnu.
	\end{equation}

	Then, the agent's must optimise their payoff with respect to
        this reference vector. Thus, instead of having to consider the
        actions of the entire population, or play individual games
        against each of their neighbours, the agent only has to
        consider $\sigma^\mu$ as a `measurement' of the local
        aggregate state and optimise with respect to this
        measurement. This allows us to make the reduction $u^\mu(\xmu,
        \xnotmu) = u^\mu(\xmu, \refmu)$. In particular, we consider
        that the agent is engaged in a matrix game against the
        reference vector so that
%
	\begin{equation}
		u^\mu(\xmu, \refmu) = \xmu \cdot A^\mu \refmu = \xmu
                \cdot A^\mu \weightedsum.
	\end{equation}
	where $A^\mu$ is the payoff matrix associated to agent
        $\mu$. Note that this means we can write the game
        $\Gamma$ with the payoff matrices $A^mu$ in place of the
        utility functions $\utility{\mu}$. The NA game allows for the
        reduction of a multiplayer game into a series of two-player
        games. The agent's goal is to maximise their payoff with
        respect to the reference vector. As such, we define the best
        response correspondence $BR^\mu$ which maps any $\refmu$ the
        set $\arg \max_{y \in \Delta_\mu} {u^\mu(y, \refmu)}$. This
        leads naturally to the definition of a Nash Equilibrium in an
        NA Game as

	\begin{definition}(NE)
		The set of vectors $\{ \NE{\mu}\}_{\mu \in \agentset}$ is an NE if, for all $\mu$,	
		\begin{equation*}
		\NE{\mu} \in \arg \max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\mu \backslash \{\bar{\mu}\}} \wmunu \NE{\nu}).
		\end{equation*}	
	\end{definition}
        \fb{It this a definition or rather a lemma?}

	We will show that such an equilibrium exists in .... Finally we note that an NA game is \emph{zero-sum} if the utilities of each agent sum to zero for any strategy set $\{ \xmu \}_{\mu \in \agentset}$. Formally

@@

	\ah{For Francesco: is it worth giving a quick introduction to Fictitious Play by talking about two player games?}
\fb{I'd rather give the definition first and then the example.}

	Fictitious Play requires that, at the current time, each agent
        considers the average behaviour of their opponent in the past
        and play a best response to that strategy. This is best
        illustrated in the two-player setting. Consider the two player
        normal form game $\Gamma_2 = (\{ 1, 2\}, ((S^1, A), (S^2,
        B)))$ so that $A$ and $B$ are the payoff matrices of agent $1$
        and $2$ respectively. As a remark, note that we can write the
        two player normal form game as an NA game simply by requiring
        that $\edgeset = \{(1, 2), (2, 1)\}$ and $\weightset$ is a 2x2
        matrix with zeros on its leading diagonal and ones on the off
        diagonal. We write the time-average of both agents' strategies
        as
%
	\begin{align}
		\alpha^\mu = \frac{1}{t} \int_0^T \xmu(t) \, dt & \text{ for $\mu \in \{1, 2\}$}
%		\alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
	\end{align}
        \fb{why using an integral rather than a simple summation?}

        \fb{decide whether you start enumerations from 1 or 0.}

	In this manner, the $\alpha^\mu(t)$ denotes the time average of the strategies played by agent
	$\mu$ up to time $t$. Then, fictitious play requires that the agents update their strategy as
	$x^1(t) \in BR^1(\alpha^2(t))$ and $x^2(t) \in
	BR^2(\alpha^1(t))$.

	We extend this naturally to the NA game $\Gamma$ by requiring that each agent update their
	strategy according to the time average of their reference vector $\refmu$. To formalise this, we
	write
	\begin{equation}
		\avgref{\mu} = \frac{1}{t} \int_0^t \refmu(s) \; ds.
	\end{equation}

@@

@@

	\begin{assumption}
		The weighted adjacency matrix $\weightset$ is constant and \emph{row stochastic} meaning
		that the sum elements in each row of $\weightset$ is equal to one.
	\end{assumption}

	\begin{assumption}
		The payoffs are given through matrix games and, therefore, are bilinear.
	\end{assumption}

	\begin{assumption}
		The cardinality of each action set $|\actionset{\mu}|$ is equal for all agents.
	\end{assumption}

	\begin{assumption}
		The NA game is zero-sum in the sense that $\sum_{\mu} u^\mu(\xmu, \weightedsum)$ for any set
		of states $(x^\mu)_{\mu \in N^\mu}$
	\end{assumption}

\fb{discuss how restrictive each of these assumptions is.}

@@

	\subsection{Existence of the Nash Equilibrium}

@@

	which is precisely the NA-Nash Equilibrium condition. This leads to the next result

@@

	\section{Convergence to the CCE set}

	In this section we aim to find some convergence structure for the case in which the NA game is not zero-sum. In particular, we  show that the NA-CTFP process converges to the set of coarse correlated equilibria. So first I will define what this means.

	The notion of the CCE set is best considered through \emph{regret} which, for agent $\mu$ we define as

	\begin{equation}
		R^{\mu} = \max_{x_{i'}^\mu \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\}
	\end{equation}

	Note, this is the \emph{average regret} for the agent $\mu$ and, of course, can be related to the \emph{cumulative regret} which is used for analysis in, e.g. (Leonardos and Piliouras, Cesa-Bianchi). To illustrate the average regret, let us consider the case where each agent has only two actions. Then $u^{\mu}(x^\mu(t), \sigma(t))$ is given by

@@

	On the other hand, let us consider that agent $\mu$'s first strategy maximises $u^{\mu}(x_{i'}^\mu(t), \sigma(t))$, then

	\begin{equation}
		\max_{x_{i'}^\mu \in S^\mu} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) = \sum_{ij} a_{1j} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{11} x_2^\mu \sigma_1^\mu + a_{12} x_2^\mu \sigma_2^\mu 
	\end{equation}

	By comparing the two expanded expressions, we can see that the latter gives the reward that agent $\mu$ would have received had they played action $1$ throughout the entire play, assuming that the behaviour of the other agents (encoded in $\sigma$) does not change. As such, this is a measure of agent $\mu$'s regret, in hindsight, for not playing action $1$ the entire time. An agent achives \emph{no regret} if $R^\mu$ is non-positive.
	% \begin{definition}[Coarse Correlated Equilibrium]
	% 	A distribution $D$ over action profiles $\times_{\mu} A^{\mu}$ is a \emph{coarse correlated
	% 	equilibrium} if, for
	% 	all players $\mu$ and
	% 	all
	% 	actions $i' \in A^{\mu}$

	% 	\begin{equation}
	% 		\mathbb{E}_{a \sim D}[u^{\mu}(a)] \geq \mathbb{E}_{a \sim D}[u^{\mu}(a^\mu_{i'}, a
	% 		^{- \mu})]
	% 	\end{equation}

	% \end{definition}

	\begin{theorem}
		Assuming that $w^{\mu \mu} = 0$, then for any choice of payoff matrix, agents following the NA-FP process achieve zero regret in the limit, i.e.
		\begin{equation}
			\lim_{T \rightarrow \infty} \max_{x_{i'}^\mu \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\} = 0
		\end{equation}

@@

		Then, applying the \emph{envelope theorem} we have

@@

		\ah{Note: I'm just figuring out how best to formulate the notion of the NA-CCE set and then I can add it in as a definition to say that NA-CTFP converges to this set.}
	\end{proof}

@@

	The fictitious play process in NA games requires that, at each time step, an agent takes a `measurement' of the aggregate strategy of its neighbours. It is on this measurement that they update their own strategy. It stands to reason that, in real environments, this measurement may be corrupted by noise. As such, we investigate the effect that introducing noise has on CTFP in a zero-sum NA game.

	\ah{To discuss with F before including in the document}.

	\section{Discussion}

>>>>

\theoremstyle{definition}
\newtheorem*{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{assumption}{Assumption}
\newtheorem*{remark}{Remark}

@@

\newcommand{\pure}[2]{e^{#1}_{#2}}

@@

	\begin{enumerate}
		\item Introduction: Explain the notion of a Network Aggregative Game, and Fictitious Play
		with literature on the state of the art. Assumptions made as well as summary of results
		\item Maybe? Relation with the model of Grammatico
		\item Preliminaries \begin{itemize}
			\item The Network Aggregative Game model
			\item Fictitious Play, as well as the CTFP property
		\end{itemize}
		\item Convergence of Fictitious Play \begin{itemize}
			\item Existence of the Nash Equilibrium
			\item Existence of a CTFP
			\item Convergence of CTFP to a fixed point
			\item Corrolary: when $w_{ii} = 0$ (i.e. the interaction graph is simple) CTFP converges
			to a NE
			\item Convergence of CTFP to the NA-CCE set
		\end{itemize}
		\item Numerical Experiments + Discussion \begin{itemize}
			\item Non-convergent examples
			\item Fictitious Play with Noise
		\end{itemize}
		\item Concluding Remarks
	\end{enumerate}

@@

	With the above definition, we can formalise the network aggregative (NA) game:

	\begin{definition}[Network Aggregative Game]
		A Network Aggregative game is defined as the tuple $\Gamma = (I, (\actionset{\mu},
        \utility{\mu})_{\mu \in \mathcal{N}})$, where $I$ is the interaction graph,
        $\actionset{\mu}$ and $\utility{\mu}$ refer to $\mu$'s set of actions (with cardinality
        $|\actionset{\mu}| = n$) and utility function respectively.
	\end{definition}

	We consider the \emph{state} of agent $\mu$ to be the probability vector $\xmu \in
	\mathbb{R}^n$ where $\xmu_i$ is the probability with which the agent plays action $i$. It
	should be noted that this probability vector is often referred to as $\mu$'s \emph{mixed
	strategy}. With this in mind, we can construct, as their state space, the unit simplex on
	agent $\mu$'s action set. This is given as $\Delta_\mu := \{\xmu \in \mathbb{R}^n \, : \,
	\sum_i \xmuaction{i} = 1\}$. Also associated with each agent is a utility function

	The utility function, for each agent $\mu$, is given as $u^\mu(\xmu, \xnotmu)$ in which we use
	the standard notation $-\mu$ to refer to all agents other than $\mu$. Notice that this requires
	that each agent play the same strategy against all of their neighbours. What is unique about the
	NA game is the structure of the payoffs themselves. In this format, each agent is receives a
	reference $\sigma$ which is a weighted sum of each of their neighbours
	state. Formally
%
	\begin{equation}
		\sigma^\mu = \sum_{\nu \in N^\mu} \wmunu \xnu.
	\end{equation}

	Then, the agent's must optimise their payoff with respect to this reference vector. Thus,
	instead of having to consider the actions of the entire population, or play individual games
	against each of their neighbours, the agent only has to consider $\sigma^\mu$ as a
	`measurement' of the local aggregate state and optimise with respect to this measurement.
	This allows us to make the reduction $u^\mu(\xmu, \xnotmu) = u^\mu(\xmu, \refmu)$. In
	particular, we consider that the agent is engaged in a matrix game against the
	reference vector so that
%
	\begin{equation}
		u^\mu(\xmu, \refmu) = \xmu \cdot A^\mu \refmu = \xmu
                \cdot A^\mu \weightedsum.
	\end{equation}

	where $A^\mu$ is the payoff matrix associated to agent $\mu$. Note that this means we can write
	the game $\Gamma$ with the payoff matrices $A^mu$ in place of the utility functions
	$\utility{\mu}$. The NA game allows for the reduction of a multiplayer game into a series of
	two-player games. The agent's goal is to maximise their payoff with respect to the reference
	vector. As such, we define the best response correspondence $BR^\mu$ which maps any $\refmu$
	the set $\arg \max_{y \in \Delta_\mu} {u^\mu(y, \refmu)}$.

	Finally, a central concept of game theory is that of the Nash Equilibrium, in which no rational
	agent has the incentive to deviate from their current state. This can be formalised by saying
	that all agents are playing the best response to each other.

	This leads naturally to the definition of a Nash Equilibrium in an NA Game as

	\begin{definition}(NE)
		The set of vectors $\{ \NE{\mu}\}_{\mu \in \agentset}$ is an NE if, for all $\mu$,	
		\begin{equation*}
		\NE{\mu} \in BR^\mu (\refmu) = \arg \max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\mu \backslash \{\bar{\mu}\}} \wmunu \NE{\nu}).
		\end{equation*}	
	\end{definition}

	\begin{remark}
		It can be seen that the concept of the Nash Equilibrium in the NA game is a natural
		extension of the NE in a bimatrix game $(A, B)$. In particular, if we consider an NA game
		with only two players and no self-loops then the above definition yields

		\begin{equation*}
			\NE{1} \in BR^1 (\sigma^1) = \arg \max_{x in \Delta_1} u^1 (x, \NE{2}), 
		\end{equation*}

		and similarly for $\NE{2}$. This is precisely the definition of an NE in a two player game \cite{}.
	\end{remark}

	We will show that the NE exists for an NA game in Section \ref{sec::ExistenceofNE}.

	Finally we note that an NA game is \emph{zero-sum} if the utilities of each agent sum to zero for any strategy set $\{ \xmu \}_{\mu \in \agentset}$. Formally

@@

	Fictitious Play requires that, at the current time, each agent considers the average state
	of their opponent in the past, and respond optimally (i.e. play a best response) to this state. In the case of an NA game, each agent considers their reference vector to be their
	opponent. As such, each agent $\mu$ must update their state according to the time-average of
	$\refmu$. To formalise this we write

	\begin{equation}
		\avgref{\mu} = \frac{1}{t} \int_0^t \refmu(s) \; ds.
	\end{equation}

@@

	\begin{remark}
		As an illustration, consider the NA game with two players, in which $\edgeset = \{(1, 2),
		(2, 1)\}$ and $\weightset$ is a 2x2 matrix with zeros on its leading diagonal and ones on
		the off diagonal. We write the time-average of both agents' state as

		\begin{align}
			\alpha^\mu = \frac{1}{t} \int_0^T \xmu(t) \, dt & \text{ for $\mu \in \{1, 2\}$}
	%		\alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
		\end{align}

		In this manner, the $\alpha^\mu(t)$ denotes the time average of the strategies played by
		agent $\mu$ up to time $t$. Then, fictitious play requires that the agents update their
		strategy as $x^1(t) \in BR^1(\alpha^2(t))$ and $x^2(t) \in BR^2(\alpha^1(t))$. It can be
		seen, therefore, that the CTFP in an NA game is a natural extension of CTFP in the classical
		two-player setting \cite{}.
	\end{remark}

@@

	\begin{assumption}
		The weighted adjacency matrix $\weightset$ is constant and \emph{row stochastic} meaning
		that the sum elements in each row of $\weightset$ is equal to one. This assumption is
		made to ensure that the analysis of NA games can be derived as a natural extension to the
		classical setting of two-player games. We can think of the row stochastic condition as the
		ability of each agent to prioritise the state information it receives from each of its
		neighbours. It is also a classical assumption made in the analysis of network games
		\cite{one of the network game papers} and can is straightforward to implement \cite{Eyad}.
	\end{assumption}

	\begin{assumption}
		The payoffs are given through matrix games and, therefore, are bilinear. Payoff matrices
		have a rich history in game theory and has generated a number of prototypical examples for
		economic study including the Prisoner's Dilemma game (see \cite{Axelrod} for an interesting
		implementation of this). They also allow for the design of multi-agent systems in
		computational settings, particularly in the case of task and resource allocation \cite{AGT
		and some of the Applied Game Theory Papers}. It should be noted, however, that game
		theoretic analysis is starting to consider various other forms of utility functions,
		including monotone \cite{Maryam} and convex \cite{Parise}. We believe that the analysis of
		Fictitious Play should follow in these developments and we consider it as an important area
		of future work.
	\end{assumption}

	\begin{assumption}
		\ah{I've been thinking about this a little, and I think it could be the case that
		we don't need to make this assumption at all. I will investigate this further, since I don't
		think this assumption has appeared in any of our results.} The cardinality of each action set $|\actionset{\mu}|$ is equal for all agents. This is
		a classical assumption which is made in most game theoretic settings and includes, as a
		special case, the analysis of homogeneous agents \cite{}. However, it should be noted that,
		in \cite{Ewerhart}, CTFP was analysed without this requirement.  
	\end{assumption}

	\begin{assumption}
		The NA game is zero-sum in the sense that $\sum_{\mu} u^\mu(\xmu, \weightedsum)$ for any set
		of states $(x^\mu)_{\mu \in N^\mu}$. This is, perhaps, one of the stronger assumptions in
		our analysis, and is required for the fixed point analysis. However, in Section
		\ref{sec::CCEConvergence}, we perform a regret analysis that considers the long term
		behaviour of CTFP without this assumption.
	\end{assumption}

@@

	\subsection{Existence of the Nash Equilibrium}
	\label{sec::ExistenceofNE}

@@

	which is precisely the Nash Equilibrium condition in the NA game. This leads to the next result

@@

	\section{CTFP achieves no regret}
	\label{sec::CCEConvergence}

	In this section we aim to find some convergence structure for the case in which the NA game is
	not necessarily zero-sum. In particular, we  show that the NA-CTFP process converges to the set
	of coarse correlated equilibria \cite{}.

	\begin{definition}
		A distribution $\mathcal{D}$ over the joint action set $S = \times_\mu S^\mu$ is
		called a \emph{coarse correlated equilibrium} (CCE) if, for all $\mu$

		\begin{equation}
			\mathbb{E}_{s \sim \mathcal{D}}[u^\mu (s^\mu, s^{- \mu})] \geq \mathbb{E}_{x \sim \mathcal{D}}[u^\mu (j, s^{- \mu})] \hspace{1cm} \forall j \in S^\mu.
		\end{equation}
	\end{definition}

	In words, the above definition says that, if the agents are given a probability distribution
	with which the can play their actions, then the expected payoff, for all agents is greater than
	or equal to the payoff that they would get by playing any of their other available actions,
	assuming that the other agents keep to the distribution.

	For an NA game, if a set of actions $s = (s^1, \ldots, s^N)$ is drawn from a joint probability
	distribution $\mathcal{D}$, then there is a corresponding set of reference vectors $\sigma =
	(\sigma^1, \ldots, \sigma^N)$, where $\sigma^\mu = \sum_{\nu \in N^\mu} \wmunu s^\nu$.
	Therefore, $\mathcal{D}$ is a probability distribution over all actions and all references.
	Consider, then, a vector of joint distributions over actions and references which is generated
	by CTFP. In particular, if by playing with CTFP, the agents reach the state $(\xmu)_{i = 1}^N$
	with references $(\refmu)_{i = 1}^N$, this is the vector $\mathcal{D} = (\mathcal{D}^1, ...,
	\mathcal{D}^N)$ such that $(\mathcal{D}^\mu)_{ij} = \xmu_i \refmu_j$. Then, the expected payoff
	that the agent would receive for playing this strategy is

	\begin{align}
		u^\mu(\xmu, \refmu) & = \xmu \cdot A^\mu \refmu \nonumber \\
		& = \sum_{i, j} (A^\mu)_{ij} \xmu_i \refmu_j \nonumber 
	\end{align}

	As such, we would say that CTFP has converged to the set of CCE if, in the limit of $t
	\rightarrow \infty$, we have that for all $\mu$

	\begin{equation}
		u^\mu (\xmu, \refmu) \geq u^\mu(i', \refmu) \hspace{1cm} \forall i' \in S^\mu.
	\end{equation}

	\begin{remark}
		As usual, the notion of CCE in an NA game is a natural extension of the CCE for two player
		games. In fact, if we consider the NA game to be a two player game with no self-loops, then
		we recover exactly the definition of the CCE set in two player games \cite{PayoffPerformance}.
	\end{remark}

	\begin{remark}
		The notion of the CCE set is related to the idea of \emph{average external regret} (for the
		sake of brevity we drop the term `external' and refer the reader to \cite{AGT}). Here, we
		will present what is meant by average regret and state that if at some time $T$ all agents'
		average regret is non-positive, then the game is said to have reached the CCE set. The
		reader should consult \cite{PayoffPerformance} for an excellent exposition regarding the
		link between the CCE set and average regret in two player games which, of course, extends
		naturally to the NA game.

		Average regret, for agent $\mu$ is defined as

		\begin{equation}
			R^{\mu} = \max_{i' \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(\pure{\mu}{i'}, \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\},
		\end{equation}

		in which $\pure{\mu}{i}$ denotes the probability vector in $\Delta_\mu$ with $1$ in the slot
		$i'$ and $0$ everywhere else. Note, this is the \emph{average regret} for the agent $\mu$
		and, of course, can be related to the \emph{cumulative regret} which is used for analysis
		in \cite{Leonardos and Piliouras, Cesa-Bianchi}.  To illustrate the average regret, let us
		consider the case where each agent has only two actions. Then $u^{\mu}(x^\mu(t), \sigma(t))$
		is given by

@@

		On the other hand, let us consider that agent $\mu$'s first strategy maximises $u^{\mu}(\pure{\mu}{1}, \sigma(t))$, then

		\begin{equation}
			u^{\mu}(\pure{\mu}{1}, \sigma(t)) = \sum_{ij} a_{1j} x_i^\mu \sigma_j^\mu = a_{11} x_1^\mu \sigma_1^\mu + a_{12} x_1^\mu \sigma_2^\mu + a_{11} x_2^\mu \sigma_1^\mu + a_{12} x_2^\mu \sigma_2^\mu 
		\end{equation}

		By comparing the two expanded expressions, we can see that the latter gives the reward that agent $\mu$ would have received had they played action $1$ throughout the entire play, assuming that the behaviour of the other agents (encoded in $\sigma$) does not change. As such, this is a measure of agent $\mu$'s regret, in hindsight, for not playing action $1$ the entire time. An agent achives \emph{no regret} if $R^\mu$ is non-positive.
	\end{remark}

	\begin{theorem}
		Assuming that $w^{\mu \mu} = 0$, then for any choice of payoff matrix, agents following the
		CTFP process achieve \emph{no regret} in the limit $t \rightarrow \infty$, i.e.
		\begin{equation}
			\lim_{T \rightarrow \infty} \max_{x_{i'}^\mu \in S^\mu} \Big\{ \frac{1}{T} \int_{0}^{T} u^{\mu}(x_{i'}^\mu(t), \sigma(t)) - u^{\mu}(m^\mu(t), \sigma(t)) \, dt \Big\} = 0
		\end{equation}

		In particular, CTFP in an NA game converges to the set of CCE.

@@

		Then, applying the \emph{envelope theorem} \cite{} we have

@@

@@

	The fictitious play process in NA games requires that, at each time step, an agent takes a
	`measurement' of the aggregate strategy of its neighbours. It is on this measurement that they
	update their own strategy. It stands to reason then, that in real environments this measurement
	may be corrupted by noise. As such, we investigate the effect that introducing noise has on CTFP
	in a zero-sum NA game.

	Noisy Experiments
	\begin{enumerate}
		\item Large (p = 20) game with noise, vary the amount of noise to see at what point we break
		convergence. Main questions: \begin{itemize}
			\item At what point do we stop reaching the NE?
			\item Does it start converging to something else, or just go haywire?
			\item Would increasing the number of iterations make it converge again?
		\end{itemize}

		\item 3 Player chain. Vary the amount of noise to see the qualitative change in behaviour.
		Main questions \begin{itemize}
			\item At what point does periodic behaviour break?
			\item Do we actually always converge towards the NE?
			\item Does this happen for all periodic behaviour?
		\end{itemize}
	\end{enumerate}
